\section{Executive summary}

\paragraph{Conclusion \& recommendation:}
Pilot an MVP of the \emph{Solar Readiness Brief} (see  section \ref{proposalOutline}) with 3-5 housing associations in Roskilde. The MVP produces a two-page, decision-ready brief per address, with transparent assumptions and citations, simple economics, and 8760-based self-consumption bands. In parallel, collaborate with Roskilde Municipality on building stock portfolio screening.

\textbf{Success criteria:} time-to-brief $\leq$ 5 minutes; annual-yield accuracy within $\pm 15\%$ vs.\ references; $\geq 30\%$ conversion from brief to pilot/quote.

\paragraph{The problem:}
Boards in housing associations lack \emph{comparable, decision-ready} material to evaluate rooftop PV and energy-community options. Data is scattered across public tools, causing delays, inconsistent assumptions, and stalled initiatives. Residents also lack a credible, General Assembly (GA)-ready brief to place PV on the agenda.

\paragraph{Proposed solution:}
A web-based \emph{Solar Readiness Brief} that turns any address into a two-page, source-linked pre-feasibility note in minutes. The brief reports indicative PV capacity and annual yield, 8760-based self-consumption/export bands, simple CAPEX/OPEX and payback, plus clearly stated assumptions and data lineage. The same engine supports \emph{portfolio screening} so municipalities can surface and prioritise high-potential roofs.

\paragraph{Benefits for key stakeholders:}
\begin{itemize}
    \item \textbf{Housing association boards}

\begin{itemize} 
  \item \textbf{Faster decisions:} decision-ready brief per address in $\leq$ 5 minutes; easy inclusion on GA agendas.
  \item \textbf{Comparable \& trusted:} standardised assumptions with sources and ranges enable apples-to-apples comparisons.
  \item \textbf{Lower pre-tender risk:} clear CAPEX/OPEX and payback shorten quote cycles with installers/EPCs.
\end{itemize}
\end{itemize}

\begin{itemize}
    \item \textbf{Roskilde Municipality}
    \begin{itemize}
  \item \textbf{Portfolio view:} screen and prioritise high-potential roofs citywide.
  \item \textbf{Consistent \& report-ready:} harmonised method; CSV/PDF outputs for climate-plan KPIs.
  \item \textbf{Operational efficiency:} earlier coordination with the distribution system operator (DSO) on expected PV capacity/export, and fewer information requests from citizens and boards.
\end{itemize}
\end{itemize}
\begin{flushleft}
\footnotesize\emph{Authorship note: Generative AI was used as a writing aid throughout this document for drafting and editing. The authors reviewed and verified all content and accept full responsibility for the results.}
\end{flushleft} 
\clearpage
